---
title: "Data explore"
format: html
editor: source
---

## Cross chapter TT 

### Some useful R packages for TT

```{r}
# install.packages("tidytuesdayR")
# install.packages("here")
# install.packages("tidyverse")
# install.packages("janitor")

library(tidytuesdayR) # For loading TT weekly releases into R
library(here) # For pain-free project directory navigation 
library(tidyverse) # A data scientist's toolbelt for wrangling and visualising your data
library(skimr) # Get a sense of your data
library(janitor) # For cleaning data
```

### Load data

TT data is released weekly (Wednesday in Australia) at this [repository](https://github.com/rfordatascience/tidytuesday) 

We will be wrangling with data from 2025-04-29 featuring the useR! 2025 program. useR! is a data science conference that brings together R users, developers, and enthusiasts from around the world for three days of tutorials, presentations, and networking. For more info, check out the [README](https://github.com/rfordatascience/tidytuesday/blob/main/data/2025/2025-04-29/readme.md) for the datasest

```{r}
# Load data using the tidytuesdayR package by providing the date the data was released
tt_data <- tt_load("2025-04-29")

# Printing the tt_data object will give you a quick overview of the data
tt_data

# The data is stored in the element `user2025`
user_data <- tt_data$user2025
user_data
```

### Get a sense of the data

Lots of categorical variables

```{r}
glimpse(user_data)
skim(user_data)
```

### Idea: What are the major keywords and how many talks have used them? 

This will be a lot of string wrangling! 

```{r}
# Create a list column
user_data <- user_data |> 
  mutate(keywords_vec = str_split(keywords, ","))

# Pivot long this list with some variables I want
user_subset <- user_data |> 
  select(session:title, speakers, keywords_vec) |> 
  unnest(keywords_vec)


```

